Efficient Handling of String-Number Conversion

### 2019-11-23 evaluation.tex
update experiments

In {\tool}, we use the following PFA selection strategy: we select PFAs of size $m$ for string variables involved in a number-string conversion constraint and PFAs with $p$ loops of size $q$ for other variables. Initially, we set $(m,p,q)=(X,X,X)$, and increase each of them by one if more precise refinement is required. We set an upper bound $7$ for each parameters and report UNKNOWN if a solution cannot be found within the bound. \yfc{need to check with Diep for the parameters}.

The way our theory solver and Z3 interacts is almost standard. Every time when Z3 asks our theory solver a string constraint satisfiability problem, our solver tries to prove it SAT or UNSAT using the aforementioned procedure. For under-approximation, every time when a corresponding linear formula is created, we create a new Z3 solver instance to solve it. If our theory solver reports UNKNOWN, Z3 remembers it in a global flag \textsf{incomplete} and tries another solution branch. If Z3 completes the search of all solution branches, it reports UNSAT if the flag \textsf{incomplete} is down, and UNKNOWN otherwise.

We compare {\tool} with other state-of-the-art string solvers, namely CVC4~(45bcf28a)~\cite{cvc4Tool}, Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3-str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}, and \textsf{Trau+}~\cite{abdulla2019chain}. We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks. We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints) and Ostrich~\cite{chen2019decision}, because most of our benchmarks contain non-trivial equality constraints, which is not fully supported by those solvers.

@@

In the second experiment, we compare with tools supporting string-number conversion on the benchmarks collected from the symbolic executor \texttt{Py-Conbyte}\footnote{\url{https://github.com/spencerwuwu/py-conbyte}}, which has the supports of string-number conversion. We ran it on several examples collected from the LeetCode platform and from Python core libraries. We also have examples that encode execution paths of some JavaScript programs (the Luhn algorithm and some array manipulation).

@@

\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, Z3, Z3-str3 and Trau+ on Basic String Constraint benchmarks.}
\scalebox{0.85}{
\begin{tabular}{|l r | r r r r r|}
\hline
\multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3-str3 & Trau+  \\ \hline
\multirow{3}{*}{PyEx}		& SAT      &  21410  & 19763 & 16528 &  3030 & 19149 \\ 
							& UNSAT    &   3883  &  3834 &  3831 &  3836 & 3828 \\
							& $\times$ &    128  &  1824 &  5062 & 18555 & 2444 \\ \hline
\multirow{3}{*}{APLAS}		& SAT      &    131  &   205 &    12 &    37 & 132 \\
							& UNSAT    &    288  &   221 &   100 &   111 & 82 \\
							& $\times$ &    181  &   174 &   488 &   452 & 386 \\ \hline
\multirow{3}{*}{LeetCode}	& SAT      &    880  &   859 &   881 &   670 & 778 \\
							& UNSAT    &   1786  &  1785 &  1785 &  1780 & 1827 \\
							& $\times$ &      0  &    22 &     0 &   216 & 61 \\ \hline
\multirow{3}{*}{StringFuzz}	& SAT      &    498  &   671 &   264 &   491 & 688 \\
							& UNSAT    &    319  &   240 &   186 &   192 & 339 \\
							& $\times$ &    248  &   154 &   615 &   382 & 38 \\\hline
\multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 11 & 11 &   12 &     8 & 247 \\
							& UNSAT    &    820  &   818 &   808 &   772 & 500 \\
							& $\times$ &      4  &     6 &    15 &    55 & 88 \\ \hline
\multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13 & 8 &     5 &    17 & 311 \\
							& UNSAT    &   1031  &   936 &  1021 &   958 & 596 \\
							& $\times$ &      1  &   101 &    19 &    70 & 138 \\ \hline
\multirow{3}{*}{Total} 		& SAT      &  22943  & 21517 & 17702 &  4253 & 21305  \\
							& UNSAT    &   8127  &  7834 &  7731 &  7649 & 7172  \\
							& $\times$ &    562  &  2281 &  6199 & 19730 & 3155  \\\hline	
\end{tabular}}
\label{table:base_benchmark}
\end{table}

>>>>

In {\tool}, we use the following PFA selection strategy. First, we use \emph{numeric PFAs} for string variables appeared in string-number conversion and \emph{standard PFAs} for others. Then we select size $m$ for numeric PFAs and $p$ loops of size $q$ for standard PFAs. Initially, we set $(m,p,q)=(5,2,q)$, where $q$ is dynamic and achieved from our internal static analysis. We double $m$, increase $p$ and $q$ by one if more precise refinement is required. We set an upper bound for each parameter and report UNKNOWN if a solution cannot be found within the bound.

The way our theory solver and Z3 interacts is almost standard. Every time when Z3 asks our theory solver a string constraint satisfiability problem, our solver tries to prove it SAT or UNSAT using the aforementioned procedure. For under-approximation, every time when a corresponding linear formula is created, we attach the current value of $m$, $p$, $q$ with the formula, and then push it to Z3 core. If our theory solver reports UNKNOWN, Z3 remembers it in a global flag \textsf{incomplete} and either tries another solution branch, or the same solution branch with different value of $m$, $p$, $q$. If Z3 completes the search of all solution branches, it reports UNSAT if the flag \textsf{incomplete} is down, and UNKNOWN otherwise.

We compare {\tool} with other state-of-the-art string solvers, namely CVC4~(45bcf28a)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3-str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}. We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks. We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{abdulla2019chain}, because they do not support all string functions in our benchmarks, especially string-number conversion.

@@

In the second experiment, we compare with tools supporting string-number conversion on the benchmarks collected from the symbolic executor \texttt{Py-Conbyte}\footnote{\url{https://github.com/spencerwuwu/py-conbyte}}, which has the supports of string-number conversion. We ran it on several examples collected from the LeetCode platform and from Python core libraries, which involve diverse usages of string-number conversion in Python such as parsing date-time, verifying and restoring IP addresses from strings, etc. We also have examples that encode execution paths of some JavaScript programs (the Luhn algorithm and some array manipulation).

@@

\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, Z3, Z3-str3 and Trau+ on Basic String Constraint benchmarks.}
\scalebox{0.85}{
\begin{tabular}{|l r | r r r r |}
\hline
\multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3-str3 \\ \hline
\multirow{3}{*}{PyEx}		& SAT      &  21410  & 19763 & 16528 &  3030 \\ 
							& UNSAT    &   3883  &  3834 &  3831 &  3836 \\
							& $\times$ &    128  &  1824 &  5062 & 18555 \\ \hline
\multirow{3}{*}{APLAS}		& SAT      &    131  &   205 &    12 &    37 \\
							& UNSAT    &    288  &   221 &   100 &   111 \\
							& $\times$ &    181  &   174 &   488 &   452 \\ \hline
\multirow{3}{*}{LeetCode}	& SAT      &    881  &   859 &   881 &   670 \\
							& UNSAT    &   1785  &  1785 &  1785 &  1780 \\
							& $\times$ &      0  &    22 &     0 &   216 \\ \hline
\multirow{3}{*}{StringFuzz}	& SAT      &    498  &   671 &   264 &   491 \\
							& UNSAT    &    319  &   240 &   186 &   192 \\
							& $\times$ &    248  &   154 &   615 &   382 \\\hline
\multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 11 & 11 &   12 &     8 \\
							& UNSAT    &    820  &   818 &   808 &   772 \\
							& $\times$ &      4  &     6 &    15 &    55 \\ \hline
\multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13 & 8 &     5 &    17 \\
							& UNSAT    &   1031  &   936 &  1021 &   958 \\
							& $\times$ &      1  &   101 &    19 &    70 \\ \hline
\multirow{3}{*}{Total} 		& SAT      &  22943  & 21517 & 17702 &  4253 \\
							& UNSAT    &   8127  &  7834 &  7731 &  7649 \\
							& $\times$ &    562  &  2281 &  6199 & 19730 \\\hline	
\end{tabular}}
\label{table:base_benchmark}
\end{table}
